
## 20 spectra collected from each side of the battery, there are 10 seconds time interval between each spectrum collection. 
The spectra quality is low, so the result is not conclusive. 
The resolution and signal to noise ratio of Raman may be decreased by switch to a different laser source on my side. 
But, we still need to find a way to prevent the battery electrolyte leaking or evaporatin to get better result. 

```{r package loading, message=FALSE, warning=FALSE}
library(tidyverse)
library(baseline)
library(plotly)
```

```{r}

pos<-read.delim("E:\\Tufts\\data\\table1.txt",
                head=F,col.names = c("wtno",c(1:20)))


posm<-pos %>% 
  select(-1) %>% 
  as.matrix()%>% 
  t() %>% 
  baseline.modpolyfit(degree = 1, tol = 0.001, rep = 100)
```


# Plot the full spectra of all spectra collected at the positive side of the battery
```{r}
posm$corrected %>% 
  t() %>% 
  as.data.frame() %>% 
  cbind(pos$wtno)%>% 
  pivot_longer(cols=starts_with("V"),names_to = c("obs")) %>%
  mutate(obs=(str_replace(obs,"V",""))) %>% 
  set_names(c("wtno","obs","value"))%>% 
  ggplot()+
  geom_line(aes(wtno,value,group=obs,color=obs))+
#  xlim(700,900)+
  ylim(0,25) 
 
wtno<-as.numeric(pos$wtno) 
```

# plot the ratio of peak around (803 cm-1 to 815 cm-1) to peak around (864 cm-1 to 875-1) for the spectra collected from the positive side of the battery
```{r}

posw<-posm$corrected %>% 
  as.data.frame(row.names=c(1:20))
posw %>% 
  set_names(pos$wtno) %>% 
  mutate(sp1=rowSums(posw[,which((wtno>803)&(wtno<815))]),
         sp2=rowSums(posw[,which((wtno>864)&(wtno<875))]),
         ratio=sp1/sp2,obs=c(1:20)) %>% 
  select(ratio,obs) %>% 
  ggplot()+
  geom_line(aes(obs,ratio))
# %>% 


# pos %>% 
#   ggplot(aes(wtno,value))+
#   geom_line(aes(group=obs,color=obs))+
#   xlim(780,900)+
#   ylim(950,975)
  
neg<-read.delim("E:\\Tufts\\data\\table3.txt",
                head=F,col.names = c("wtno",c(1:20)))
negm<-neg %>% 
  select(-1) %>% 
  as.matrix()%>% 
  t() %>% 
  baseline.modpolyfit(degree = 1, tol = 0.001, rep = 100)
```


# Plot the full spectra of all spectra collected at the negtive side of the battery
```{r}
negm$corrected %>% 
  t() %>% 
  as.data.frame() %>% 
  cbind(pos$wtno)%>% 
  pivot_longer(cols=starts_with("V"),names_to = c("obs")) %>%
  mutate(obs=(str_replace(obs,"V",""))) %>% 
  set_names(c("wtno","obs","value"))%>% 
#  filter(obs %in% c("1","5","10","15","20")) %>% 
  ggplot()+
  geom_line(aes(wtno,value,group=obs,color=obs))+
#  xlim(700,900)+
  ylim(0,80) 
```

# Plot the spectra at 700cm-1 to 900cm-1 region of all spectra collected at the negtive side of the battery
```{r}
negm$corrected %>% 
  t() %>% 
  as.data.frame() %>% 
  cbind(pos$wtno)%>% 
  pivot_longer(cols=starts_with("V"),names_to = c("obs")) %>%
  mutate(obs=(str_replace(obs,"V",""))) %>% 
  set_names(c("wtno","obs","value"))%>% 
#  filter(obs %in% c("1","5","10","15","20")) %>% 
  ggplot()+
  geom_line(aes(wtno,value,group=obs,color=obs))+
  xlim(700,900)+
  ylim(0,80) 
```


# plot the ratio of peak around (803 cm-1 to 815 cm-1) to peak around (864 cm-1 to 875-1) for the spectra collected from the negtive side of the battery
```{r}
negw<-negm$corrected %>% 
  as.data.frame(row.names=c(1:20))
negw %>% 
  set_names(pos$wtno) %>% 
  mutate(sp1=rowSums(negw[,which((wtno>803)&(wtno<815))]),
         sp2=rowSums(negw[,which((wtno>864)&(wtno<875))]),
         ratio=sp1/sp2,obs=c(1:20)) %>% 
  select(ratio,obs) %>% 
  ggplot()+
  geom_line(aes(obs,ratio))
```



